\Large \bf Uncovering Bugs in Distributed Storage Systems during\\Testing (not in Production!)

### 2015-09-21 evaluation.tex

For the MigratingTable case study, we evaluated the \psharp test harness of \S\ref{sec:cases:migration} on 11 ``bugs'', including 8 that actually occurred in development and 3 other code changes that we deemed interesting ways of making the code incorrect. The test found seven of the bugs, which are listed first in Table~\ref{tab:testing}. The remaining four bugs (denoted with $\diamond$) were not caught with our default test harness in the 100,000 iterations (a process that required less than 30 minutes). We believe this is because the inputs and schedules that trigger them are too rare in our distribution. To confirm this, we wrote a custom test case for each bug with a specific input that triggers it and were able to quickly reproduce the bugs, as shown. This method is useful for regression testing, but one could not use it during development with no prior knowledge about the bugs.

>>>>

For the MigratingTable case study, we evaluated the \psharp test harness of \S\ref{sec:cases:migration} on 11 ``bugs'', including 8 \emph{organic} bugs that actually occurred in development and 3 \emph{notional} bugs (marked $*$), which are other code changes that we deemed interesting ways of making the code incorrect. The test found seven of the organic bugs, which are listed first in Table~\ref{tab:testing}. The remaining four bugs (denoted with $\diamond$) were not caught with our default test harness in the 100,000 iterations (a process that required less than 30 minutes). We believe this is because the inputs and schedules that trigger them are too rare in our distribution. To confirm this, we wrote a custom test case for each bug with a specific input that triggers it and were able to quickly reproduce the bugs, as shown. This method is useful for regression testing, but one could not use it during development with no prior knowledge about the bugs.

### 2015-09-21 intro.tex

Developers of production distributed systems use many testing techniques, such as unit testing, integration testing, stress testing, and fault injection. In spite of extensive use of these testing methods, many bugs that arise from subtle combinations of concurrency and failure events are missed during testing and get exposed only after a system has been put into production. However, allowing bugs to reach production, before they are found and fixed, can cost organizations a lot of money~\cite{tassey2002economic} and lead to customer dissatisfaction~\cite{amazon2012aws, google2014outage}.

We interviewed technical leaders and senior managers in the Microsoft Azure team regarding the top problems in distributed system development. The consensus was that one of the most critical problems today is how to improve \emph{testing coverage} to find bugs \emph{before} a system goes to production. The need for better testing techniques is not specific to Microsoft; other companies, such as Amazon and Google, have acknowledged~\cite{chandra2007paxos,newcombe2015aws} that testing methodologies have to improve to be able to reason about the correctness of increasingly more complex distributed systems that are used in production.

Recently, engineers in Amazon Web Services (AWS) described their use of formal methods ``to prevent serious but subtle bugs from reaching production''~\cite{newcombe2015aws}. The gist of their approach is to extract the high-level logic from a production system, represent this logic as specifications in the expressive TLA+~\cite{lamport1994temporal} language, and finally verify the specifications using a model checker. While highly effective, as demonstrated by its use in AWS, this approach falls short of ``verifying that executable code correctly implements the high-level specification'', and the AWS team admits that it is ``not aware of any such tools that can handle distributed systems as large and complex as those being built at Amazon''~\cite{newcombe2015aws}.

>>>>

Developers of production distributed systems use many testing techniques, such as unit testing, integration testing, stress testing, and fault injection. In spite of extensive use of these testing methods, many bugs that arise from subtle combinations of concurrency and failure events are missed during testing and get exposed only in production. However, allowing serious bugs to reach production can cost organizations a lot of money~\cite{tassey2002economic} and lead to customer dissatisfaction~\cite{amazon2012aws, google2014outage}.

We interviewed technical leaders and senior managers in Microsoft Azure regarding the top problems in distributed system development. The consensus was that one of the most critical problems today is how to improve \emph{testing coverage} so that bugs can be uncovered \emph{during testing} and \emph{not in production}. The need for better testing techniques is not specific to Microsoft; other companies, such as Amazon and Google, have acknowledged~\cite{chandra2007paxos,newcombe2015aws} that testing methodologies have to improve to be able to reason about the correctness of increasingly more complex distributed systems that are used in production.

Recently, the Amazon Web Services (AWS) team used formal methods ``to prevent serious but subtle bugs from reaching production''~\cite{newcombe2015aws}. The gist of their approach is to extract the high-level logic from a production system, represent this logic as specifications in the expressive TLA+~\cite{lamport1994temporal} language, and finally verify the specifications using a model checker. While highly effective, as demonstrated by its use in AWS, this approach falls short of ``verifying that executable code correctly implements the high-level specification'', and the AWS team admits that it is ``not aware of any such tools that can handle distributed systems as large and complex as those being built at Amazon''~\cite{newcombe2015aws}.
